Torontonians Prefer to Get Married in the Warmer Half of the Year

### 2024-01-24 outputs/paper/paper.qmd
updates

marriage_data |>
  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
  geom_point() +
  geom_text(hjust=0, vjust=0) +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
  labs(x = "Month", y = "Marriages", color = "Country")
```
```{r}
#| echo: false
#| message: false
#| include: false
marriage_data_2022 <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
summary(marriage_data_2022$Marriages)
sum(marriage_data_2022$Marriages)
```

@@

marriage_data |>
  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
  geom_point() +
  geom_text(hjust=0, vjust=0) +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
  labs(x = "Month", y = "Marriages", color = "Country")
```

@@

marriage_data |>
  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
  geom_point() +
  geom_path(color = 'red') +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
  labs(x = "Month", y = "Marriages", color = "Country")
```
Combining both years, we generate another graph to plot the number of marriage licenses and connect the points with a line so the trend over time is easier to see. It is important to note that the line only connect the points and do not represent the rate of change. This cyclical nature of more marriage licenses obtained in warm months is evident (@fig-marriages)

>>>>

marriage_data$Date <- factor(marriage_data$Date, levels = unique(marriage_data$Date))

marriage_data |>
  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
  geom_point() +
  geom_text(hjust=0, vjust=0) +
  scale_x_discrete(breaks=c("2022-January-01","2022-April-01","2022-July-01", "2022-October-01")) +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
  labs(x = "Month", y = "Marriages", color = "Country")
```
```{r}
#| echo: false
#| message: false
#| include: false
marriage_data_2022 <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
summary(marriage_data_2022$Marriages)
sum(marriage_data_2022$Marriages)
```

@@

marriage_data$Date <- factor(marriage_data$Date, levels = unique(marriage_data$Date))

marriage_data |>
  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
  geom_point() +
  geom_text(hjust=0, vjust=0) +
  scale_x_discrete(breaks=c("2022-January-01","2022-April-01","2022-July-01", "2022-October-01")) +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
  labs(x = "Month", y = "Marriages", color = "Country")
```

@@

marriage_data$Date <- factor(marriage_data$Date, levels = unique(marriage_data$Date))

marriage_data |>
  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
  scale_x_discrete(breaks=c("2022-January-01","2022-June-01","2023-January-01", "2023-June-01")) +
  labs(x = "Month", y = "Marriages", color = "Country")
```
Finally, I plotted both 2022 and 2023 together so the trend over time is easier to see. This cyclical nature of more marriage licenses obtained in warm months is evident (@fig-marriages).
